Spatial Reasoning and Data Displays

### 2015-06-27 Paper/InfoVis2015Revision/TestingVisualAptitude.Rnw
study procedure a bit later

\paragraph{Experimental Procedure}
All tasks (cognitive and lineups) were provided to participants on paper \newtext{in a supervised lab setting}, to conform to the procedure used in~\cite{ekstrom1976manual}. The order of tasks was the same for each participant due to the constraints of in-person testing; results from an internal pilot tests with a counterbalanced design did not indicate an effect of task order, nor was there any indication in the results of an interaction/learning effect from one task to the next.

Between cognitive tasks, participants were also asked to complete three blocks of 20 lineups each, assembled from previous studies~\cite{hofmann2012graphical,majumder2013validation}. Participants were given 5 minutes to complete each block of 20 lineups. Figure~\ref{fig:lineup}(a) shows a sample lineup of box plots.

>>>>

\paragraph{Experimental Procedure}
All tasks (cognitive and lineups) were provided to participants on paper \newtext{in a supervised lab setting}, to conform to the procedure used in~\cite{ekstrom1976manual}. The order of tasks was the same for each participant due to the constraints of in-person testing; an internal pilot study did not indicate an effect of task order, \newtext{nor did the pilot results suggest an interaction/learning effect from one task to the next.}

Between cognitive tasks, participants were asked to complete three blocks of 20 lineups each, assembled from previous studies~\cite{hofmann2012graphical,majumder2013validation}. Participants were given 5 minutes to complete each block of 20 lineups. Figure~\ref{fig:lineup}(a) shows a sample lineup of box plots.
